---
title: "2023-06-29-3rd-Blog-Post"
author: "Kristina Golden"
date: "2023-06-30"
output: 
  github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rmarkdown)
library(caret)
library(corrplot)
setwd('C:/Users/kmgolden/Documents/GitHub/Main_Respository/kgolden4514.github.io/_Rmd')
library(AppliedPredictiveModeling)
library(gendata)
library(simstudy)
library(data.table)
library(ggplot2)
library(survminer)
library(survival)
```

Create a new .Rmd file where you will write the content of the post.  This should be in your _Rmd folder and you'll need to mimic much of what was done in blog post 2

Write a post about what you consider the coolest thing you've learned about programming in R.  Include an example of it (or at least the code to do it) in your post (for instance, if it was ggplot you could read in a data set and create a cool plot).

Graphically, the coolest thing I have learned in R is the bubble graph that graphs the correlations between multiple variables. The bubble graph is a very interesting visual that allows the person doing the analyses to make a quick determination between two or more variables that are highly correlated. Computationally the coolest thing I have learned is the weibull distribution and how to use it. In my internship, I am using the weibull distribution to examine failure rates for different components on the H-53K helicopter. We do this by looking at beta. It is extremely interesting! I am really enjoying applying my knowledge of R language and R code to analyze data that I pulled myself and cleaned myself. Not only am I pulling the data, programming it, and anlayzing it, I also get to make a recommendation about the preventative inspection interval for different components of the aircraft. After the data cleaning, the rest of steps are completed in R.

```{r}
# The Abalone data consist of data from 4177 abalones. The data consist of measurements of the type (male, female and infant), the longest shell measurement, the diameter, height and several weights (whole, shucked, viscera and shell). The outcome is the number of rings. The age of the abalone is the number of rings plus 1.5.
abalone <- data.frame(abalone)
abalone$age <- abalone$Rings + 1.5
```

I am going to make a bubble plot with the response variable being the age of the abalone. I am going to take out the rings variable, because obviously that is going to be highly correlated with the age of the abalone. I will also remove the type because it is not a numerical variable.

#  Correlation Plot
```{r}
#Remove the rings variable
abalone <- abalone[ , -c(1, 9)]
# find correlation values
correlation <- cor(abalone, method = "spearman")
# plot the bubbles on upper-right half
corrplot(correlation, type = "upper", tl.pos = "lt", tl.col = "black", tl.cex = 0.75, tl.srt = 45, mar = c(2, 0, 1, 0))
# print values on lower-left half
corrplot(correlation, type = "lower", method = "number", add = TRUE, diag = FALSE, tl.pos = "n", number.cex = 0.75)
```
All numerical variables have very high positive correlations.

# Weibull distribution  
Because the data I use to do the weibull distributions in my internship are secured information, I have simulated one here.
```{r}
def <- defSurv(varname = "time", formula = -13.7, scale = 1, shape = 0.49)
set.seed(1134)
dd <- genData(101)
dd <- genSurv(dd, def, digits = 0)
dd$status <- 1

fit <- survfit( Surv(time, status) ~ 1, data = dd )
ggsurvplot(fit, data = dd, palette = "FFC0CB")
```

