---
title: "2023-06-29-3rd-Blog-Post"
author: "Kristina Golden"
date: "2023-06-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rmarkdown)
library(caret)
library(corrplot)
library(AppliedPredictiveModeling)
library(gendata)
library(simstudy)
library(data.table)
library(ggplot2)
library(survminer)
library(survival)
library(tidyverse)
library(ggrastr)
library(GGally)
```


Graphically, the coolest thing I have learned in R is the bubble graph that graphs the correlations between multiple variables. The bubble graph is a very interesting visual that allows the person doing the analyses to make a quick determination between two or more variables that are highly correlated. Computationally the coolest thing I have learned is the weibull distribution and how to use it. In my internship, I am using the weibull distribution to examine failure rates for different components on the H-53K helicopter. We do this by looking at beta. It is extremely interesting! I am really enjoying applying my knowledge of R language and R code to analyze data that I pulled myself and cleaned myself. Not only am I pulling the data, programming it, and anlayzing it, I also get to make a recommendation about the preventative inspection interval for different components of the aircraft. After the data cleaning, the rest of steps are completed in R.


# Correlation Bubble Chart
```{r}
setwd('C:/Users/kmgolden/Documents/GitHub/HW/HW8')
# Read in the data
bike <- read.csv('SeoulBikeData.csv')

# Make a binary variable
bike$BiRentedBC <- ifelse(bike$Rented.Bike.Count >= 700, 1,0)

# Reorder data, drop date, and rename variables
bike <- bike[, c(2, 15, 3:14)]
colnames(bike) <- c('RentedBC', 'BiRentedBC', 'Hour', 'Temp', 'Humidity', 'WindSpeed', 'Visib', 'DewPtTemp', 
                    'Rad', 'Rain',
                    'Snow','Seasons',
                    'Holiday', 'FunDay')

# Split data into train and test
train_in <- createDataPartition(1:nrow(bike), p = 0.75, list = FALSE)
train <- bike[train_in, ]
test <- bike[-train_in, ]

train2 <- train[, c(1, 3:11)]

# Set seed for reproduction
set.seed(10210526)

correlation <- cor(train2, method = "spearman")

# plot the bubbles on upper-right half
corrplot(correlation, type = "upper", tl.pos = "lt", 
         tl.col = "black", tl.cex = 0.75,
         tl.srt = 45,mar = c(2, 0, 1, 0))

# print values on lower-left half
corrplot(correlation, type = "lower", method = "number", 
         add = TRUE,
         diag = FALSE, tl.pos = "n", number.cex = 0.75)
```
# Weibull distribution  
Because the data I use to do the weibull distributions in my internship are secured information, I have simulated one here.
```{r}
def <- defSurv(varname = "time", formula = -13.7, scale = 1, shape = 0.49)
set.seed(1134)
dd <- genData(101)
dd <- genSurv(dd, def, digits = 0)
dd$status <- 1

fit <- survfit( Surv(time, status) ~ 1, data = dd )
ggsurvplot(fit, data = dd, palette = "FFC0CB")
```

